Understanding the Impact of Socioeconomic and Regional Factors on Health and Educational Outcomes

### 2024-12-09 code.qmd
changing summary to modelsummary for q2

#log-odds scale
summary(lmod,
             fmt = fmt_significant(2),
             shape = term ~ model + statistic,
             statistic = c("std.error","conf.int","p.value"),
             exponentiate = FALSE,
             gof_map=NA)

summary(lmod,
             fmt = fmt_significant(2),
             shape = term ~ model + statistic,
             statistic = c("std.error","conf.int","p.value"),
             exponentiate = TRUE,
             gof_map=NA)

@@

#log-odds scale
summary(imp_mods,
             fmt = fmt_significant(2),
             shape = term ~ model + statistic,
             statistic = c("std.error","conf.int","p.value"),
             exponentiate = FALSE,
             gof_map=NA)

summary(imp_mods,
             fmt = fmt_significant(2),
             shape = term ~ model + statistic,
             statistic = c("std.error","conf.int","p.value"),
             exponentiate = TRUE,
             gof_map=NA)
```

>>>>

#log-odds scale
modelsummary(lmod,
             fmt = fmt_significant(2),
             shape = term ~ model + statistic,
             statistic = c("std.error","conf.int","p.value"),
             exponentiate = FALSE,
             gof_map=NA)

modelsummary(lmod,
             fmt = fmt_significant(2),
             shape = term ~ model + statistic,
             statistic = c("std.error","conf.int","p.value"),
             exponentiate = TRUE,
             gof_map=NA)

@@

#log-odds scale
modelsummary(imp_mods,
             fmt = fmt_significant(2),
             shape = term ~ model + statistic,
             statistic = c("std.error","conf.int","p.value"),
             exponentiate = FALSE,
             gof_map=NA)

modelsummary(imp_mods,
             fmt = fmt_significant(2),
             shape = term ~ model + statistic,
             statistic = c("std.error","conf.int","p.value"),
             exponentiate = TRUE,
             gof_map=NA)
```
